The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
hab sel fst para

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999].
Combined, social structure and habitat selection are intimately linked as
individuals must share space to interact and the distribution of resources
influences home range size and group dynamics [@Webber_2018]. Animals select
habitats are multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.

>>>>

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources resources or features by animals [@Manly_1993; @Boyce_1999].
Combined, social structure and habitat selection are intimately linked as
individuals must share space to interact and the distribution of resources
influences group dynamics and home range size [@Webber_2018]. Animals select
habitats at multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.
